Remark on the hypothetical judgment

### 2015-08-01 paper.tex
more references
...

Thanks to Mark van Atten, Robert Harper, Clarissa Littler, and Danny Gratzer for
helpful conversations about hypothetical judgment.

\newpage
\bibliographystyle{plain}
\bibliography{refs}

>>>>

Thanks to Mark van Atten, Robert Harper, Clarissa Littler, and Danny Gratzer for
helpful conversations about hypothetical judgment, elimination rules and the bar
theorem.

\newpage

\nocite{*}
\bibliographystyle{plain}
\bibliography{refs}
